Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-30 fmics/paper.tex
Fix up proof of Theorem 3

Under such a constraint, we have proved a preliminary result bounding the error of $\mathsf{output}\;D\;n\;x\;t$ compared to $\mathsf{exact}\;D\;n\;x\;t$.
\begin{theorem}\label{max_error}
For all $k$ and $D$ satisfying $|D\;(t'+1)-D\;t'|\leq k$ at all times, the following holds for all slices $n>0$, tap positions $x$, and times $t$:
\begin{multline*}
t>(\mathsf{tap}\;n\;x+1)\times(\mathsf{delay}\;n)+\mathsf{delay}\;n+\mathsf{delay\_sum}\;n\implies\\
|\mathsf{output}\;D\;n\;x\;t-\mathsf{exact}\;D\;n\;x\;t|\leq(\mathsf{tap}\;n\;x+1)\times(\mathsf{delay\;n})\times k\times(\mathsf{delay}\;n+\mathsf{delay\_sum}\;n)
\end{multline*}
\end{theorem}
\begin{proof}
By applying Theorem~\ref{output_eq_exact}, we are left with an equation involving $\mathsf{exact}$ but not $\mathsf{output}$, specifically between $\mathsf{exact}\;D\;n\;x\;t$ and $\mathsf{exact}\;D\;n\;x\;(\mathsf{last\_update}\;n\;t+1-\mathsf{delay\_sum}\;n)$.
Our assumption on $t$ ensures that the case where the function is equal to $0$ in Theorem~\ref{output_eq_exact} or in the definition of $\mathsf{exact}$ never applies.
Now, $\mathsf{exact}$ is defined as a sum of consecutive values of $D$, so we simply need to bound the difference between one such sum and another earlier one of the same size.
If at each step the maximum difference is $k$, then the total difference is at most $k$ times the distance between the ends of the two sums, which is the bound stated in the theorem <actually the theorem may have an additional factor increasing the size of the bound, that made it easier to prove - not sure>.
\end{proof}

>>>>

Under such a constraint, we have proved a preliminary result bounding the error of $\mathsf{output}\;D\;n\;x\;t$ compared to $\mathsf{exact}\;D\;n\;x\;t$.
\begin{theorem}\label{max_error}
For all $k$ and $D$ satisfying $|D\;(t'+1)-D\;t'|\leq k$ at all times, the following holds for all slices $n>0$, tap positions $x$, and times $t$:
\begin{multline*}
t>(\mathsf{tap}\;n\;x+1)\times(\mathsf{delay}\;n)+\mathsf{delay}\;n+\mathsf{delay\_sum}\;n\implies\\
|\mathsf{output}\;D\;n\;x\;t-\mathsf{exact}\;D\;n\;x\;t|\leq(\mathsf{tap}\;n\;x+1)\times(\mathsf{delay\;n})\times k\times(\mathsf{delay}\;n+\mathsf{delay\_sum}\;n)
\end{multline*}
\end{theorem}
\begin{proof}
By applying Theorem~\ref{output_eq_exact}, we are left with an equation involving $\mathsf{exact}$ but not $\mathsf{output}$, specifically between $\mathsf{exact}\;D\;n\;x\;t$ and $\mathsf{exact}\;D\;n\;x\;(\mathsf{last\_update}\;n\;t+1-\mathsf{delay\_sum}\;n)$.
Our assumption on $t$ ensures that we are never in the $0$ case of either Theorem~\ref{output_eq_exact} or of the definition of $\mathsf{exact}$.
Now, $\mathsf{exact}$ is defined as a sum of consecutive values of $D$, so we simply need to bound the difference between one such sum and another earlier one of the same size.
But if at each step the maximum difference is $k$, then the total difference is at most $k$ times the distance between the ends of the two sums, as required.
(We use the fact that $\mathsf{last\_update}\;n\;t=t-t\operatorname{mod}\mathsf{delay}\;n$ and, in general, that $a\operatorname{mod}b<b$.)
\end{proof}
